### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e0a1165d0847969b43135297d89dacdc6dda7a11 🚀

@@

>>>>

\hypertarget{the-metaweb-is-an-inherently-probabilistic-object}{%
\section{The metaweb is an inherently probabilistic
object}\label{the-metaweb-is-an-inherently-probabilistic-object}}

@@

\hypertarget{graph-embedding-offers-promises-the-inference-of-potential-interactions}{%
\section{Graph embedding offers promises the inference of potential
interactions}\label{graph-embedding-offers-promises-the-inference-of-potential-interactions}}

\hypertarget{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}{%
\section{The metaweb embeds hypotheses about which spatial boundaries
are
meaningful}\label{the-metaweb-embeds-hypotheses-about-which-spatial-boundaries-are-meaningful}}
